---
title: "CompleteRubrumGcryoPathways"
author: "cpaight"
date: "2/10/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(janitor)
```
```{r setwd}
#complete pathways files from Kegg
#grep -E 'M[0-9]+' CompletePathwaysGcryo > GcryoPathway.txt
#sed -i -r 's/ +(M[0-9]+)(.+)(\(.+[0-9]+\/[0-9]+\))/\1\t\2\t\3/' GcryoPathway.txt
#sed -i -r 's/(.+)([0-9]+)\/([0-9]+)\)/\1\t\2\t\3/' GcryoPathway.txt
setwd("~/Documents/ComparitivePaperWork/prey/knum")
GcryoPathway <- read.delim2("~/Documents/ComparitivePaperWork/prey/knum/GcryoPathway.txt", stringsAsFactors=FALSE)
MrubrumPathway <- read.delim2("~/Documents/ComparitivePaperWork/prey/knum/MrubrumPathway.txt", stringsAsFactors=FALSE)
tMrubrumPathway <- read.delim2("~/Documents/ComparitivePaperWork/prey/knum/tMrubrumPathway.txt", stringsAsFactors=FALSE)
MchamPathway <- read.delim2("~/Documents/ComparitivePaperWork/prey/knum/MchamPathway.txt", stringsAsFactors=FALSE)
MpulexPathway <- read.delim2("~/Documents/ComparitivePaperWork/prey/knum/MpulexPathway.txt", stringsAsFactors=FALSE)
KeggTable3 <- read.delim2("~/Documents/ComparitivePaperWork/CompletePathways/matrix/KeggTable3.txt", stringsAsFactors=FALSE)
```

```{r merge df}
#GcryoPathway$GC <- 1
MrubrumPathway$pMR <- MrubrumPathway$Have/MrubrumPathway$OutOf
tMrubrumPathway$tMR <- tMrubrumPathway$Have/tMrubrumPathway$OutOf
MpulexPathway$MP <- MpulexPathway$Have/ MpulexPathway$OutOf
MchamPathway$MC <- MchamPathway$Have/ MchamPathway$OutOf
pMR <- MrubrumPathway[,c(1,6)]
tMR <- tMrubrumPathway[,c(1,6)]
MP <- MpulexPathway[,c(1,6)]
MC <- MchamPathway[,c(1,6)]
Prey <-GcryoPathway[,c(1,4:5)]
CompletePathwayTable <-merge(KeggTable3, Prey, by=c('Map'))
CompletePathwayTable <- merge(CompletePathwayTable, MP, by=c('Map'), all=T)
CompletePathwayTable <- merge(CompletePathwayTable, MC, by=c('Map'), all=T)
CompletePathwayTable <- merge(CompletePathwayTable, tMR, by=c('Map'), all=T)
CompletePathwayTable <- merge(CompletePathwayTable, pMR, by=c('Map'), all=T)
CompletePathwayTable <- CompletePathwayTable[!is.na(CompletePathwayTable$Catagory),]
write.table(CompletePathwayTable, file="~/Documents/ComparitivePaperWork/prey/knum/CompletePathwayTable.txt", sep='\t', quote=F)
#drop pathways that aren't functional
CompletePathwayTable[is.na(CompletePathwayTable)] <- 0
FunctionalPathwayTable <- CompletePathwayTable[CompletePathwayTable$MC>.5,]
FunctionalPathwayTable$sort <- FunctionalPathwayTable$MC - FunctionalPathwayTable$pMR
FunctionalPathwayTable$Raw <- FunctionalPathwayTable$OutOf * FunctionalPathwayTable$sort
write.table(FunctionalPathwayTable, file="~/Documents/ComparitivePaperWork/prey/knum/FunctionalPathwayTable.txt", sep='\t', quote=F)
```
```{r nessasary in pulec cham not in rubrum}
NeededMPMC <- CompletePathwayTable[CompletePathwayTable$MC >.75 | CompletePathwayTable$MP > .75,]
NeededColorCalc <- NeededMPMC
NeededColorCalc$MPAlpha <- NeededMPMC[,7]*255
NeededColorCalc$MCAlpha <- NeededMPMC[,8]*255
NeededColorCalc$tMRAlpha <- NeededMPMC[,9]*255
NeededColorCalc$pMRAlpha <- NeededMPMC[,10]*255
NeededColorCalc <- NeededColorCalc[,c(1:6,11:14)]
write.table(NeededColorCalc, file="~/Documents/ComparitivePaperWork/prey/knum/NeededColorCalc.txt", sep='\t', quote=F,row.names=F)
write.table(NeededMPMC, file="~/Documents/ComparitivePaperWork/prey/knum/NeededMPMC.txt", sep='\t', quote=F,row.names=F)
MissingMR <- NeededMPMC[NeededMPMC$tMR < .5| NeededMPMC$pMR < .5, ]
write.table(MissingMR, file="~/Documents/ComparitivePaperWork/prey/knum/MissingMR.txt", sep='\t', quote=F, row.names=F)
```

```{r reshape date frame to long format}
PathwaysforBOX <- FunctionalPathwayTable[,c(2,4,5,10)]
PathwaysforBOX$Have <- 1
colnames(PathwaysforBOX)[colnames(PathwaysforBOX) == 'Have'] <- 'GC'
write.table(PathwaysforBOX, file='PathwaysforBox.txt', sep='\t', quote=F, row.names=F)
```
LongPathTable2 <- PathwaysforBOX %>%  pivot_longer(-c(1), names_to = "species", values_to = "count")
widePathTable2 <- as.data.frame(t(PathwaysforBOX))
#widePathTable <- PathwaysforGraph1 %>%  pivot_wider_spec(names_from = c(Catagory), values_from= c(Specific,MP, MC, tMR, pMR))
#widePathTable <- widePathTable[c(2,1,3:6),]
widePathTable2 <- widePathTable2 %>%row_to_names(row_number = 1) %>% clean_names()
widePathTable2 <- widePathTable2 %>% select(sort(names(.)))
```
unmodified fix first

```{r PlotChrisGeneChart, fig.height=11, fig.width=8.5}
gene.dat <- widePathTable2
#par(mfrow= c(3,2))
#mar=c(4,4,2,2)
pMR <- rgb(52/255,101/255,164/255)
GC <- rgb(80/255,147/255,137/255)


Carbohydrate_metabolism.x <- c(8:23)
FA.x <- c(1:11)
AA.x <- c(1:8)

Carbohydrate_metabolism.y <- rep(16,length(Carbohydrate_metabolism.x))
FA.y <- rep(9, length(FA.x))
AA.y <- rep(2, length(AA.x))

plot(Carbohydrate_metabolism.x,Carbohydrate_metabolism.y,xlim=c(-9,20),ylim=c(-3,19),xaxt='n',yaxt='n',xlab='',ylab='')
#,type='n'
points(Carbohydrate_metabolism.x,Carbohydrate_metabolism.y,pch=22,cex=3,lwd=2,bg=c('white',pMR)[factor(t(gene.dat[1,8:23]),levels=c("0","1"))])
points(Carbohydrate_metabolism.x,Carbohydrate_metabolism.y-1,pch=22,cex=3,lwd=2,bg=c('white',GC)[factor(t(gene.dat[2,8:23]),levels=c("0","1"))])
#text(Carbohydrate_metabolism.x-.3,Carbohydrate_metabolism.y+.6,colnames(gene.dat)[1:10],srt=45,pos=4)
text(rep(min(Carbohydrate_metabolism.x)-.3,4),c(min(Carbohydrate_metabolism.y),min(Carbohydrate_metabolism.y)-1,min(Carbohydrate_metabolism.y)-2,min(Carbohydrate_metabolism.y)-3),c('M. pulex','M. chamaeleon','M. rubrum (temperate)','M. rubrum (polar)'),pos=2)
text(min(Carbohydrate_metabolism.x)-5,min(Carbohydrate_metabolism.y)+2,'Carbohydrate_metabolism',cex=1.8,col='gray50',pos=4)
```
points(FA.x,FA.y,pch=22,cex=3,lwd=2,bg=c('white',MP)[factor(t(gene.dat[1,34:44]),levels=c("0","1"))])
points(FA.x,FA.y-1,pch=22,cex=3,lwd=2,bg=c('white',MC)[factor(t(gene.dat[2,34:44]),levels=c("0","1"))])
points(FA.x,FA.y-2,pch=22,cex=3,lwd=2,bg=c('white',tMR)[factor(t(gene.dat[3,34:44]),levels=c("0","1"))])
points(FA.x,FA.y-3,pch=22,cex=3,lwd=2,bg=c('white',pMR)[factor(t(gene.dat[4,34:44]),levels=c("0","1"))])
#text(FA.x-.3,FA.y+.6,colnames(gene.dat)[11:19],srt=45,pos=4)
text(rep(min(FA.x)-.3,4),c(min(FA.y),min(FA.y)-1,min(FA.y)-2,min(FA.y)-3),c('M. pulex','M. chamaeleon','M. rubrum (temperate)','M. rubrum (polar)'),pos=2)
text(min(FA.x)-5,min(FA.y)+2.1,'Lipid Metabolism',cex=1.8,col='gray50',pos=4)


points(AA.x,AA.y,pch=22,cex=3,lwd=2,bg=c('white',MP)[factor(t(gene.dat[1,1:8]),levels=c("0","1"))])
points(AA.x,AA.y-1,pch=22,cex=3,lwd=2,bg=c('white',MC)[factor(t(gene.dat[2,1:8]),levels=c("0","1"))])
points(AA.x,AA.y-2,pch=22,cex=3,lwd=2,bg=c('white',tMR)[factor(t(gene.dat[3,1:8]),levels=c("0","1"))])
points(AA.x,AA.y-3,pch=22,cex=3,lwd=2,bg=c('white',pMR)[factor(t(gene.dat[4,1:8]),levels=c("0","1"))])
#text(AA.x-.3,AA.y+.6,colnames(gene.dat)[20:34],srt=45,pos=4)
text(rep(min(AA.x)-.3,4),c(min(AA.y),min(AA.y)-1,min(AA.y)-2,min(AA.y)-3),c('M. pulex','M. chamaeleon','M. rubrum (temperate)','M. rubrum (polar)'),pos=2)
text(min(AA.x)-5,min(AA.y)+1.6,'Amino Acid Biosynthesis',cex=1.8,col='gray50',pos=4)

cofactor.x <- c(1:5)
energy.x <- c(1:6)
#AA.x <- c(1:15)

cofactor.y <- rep(16,length(cofactor.x))
energy.y <- rep(9, length(energy.x))
#AA.y <- rep(2, length(AA.x))

plot(cofactor.x,cofactor.y,xlim=c(-5,20),ylim=c(-3,19),xaxt='n',yaxt='n',xlab='',ylab='')
#,type='n'
points(cofactor.x,cofactor.y,pch=22,cex=3,lwd=2,bg=c('white',pulexcol)[factor(t(gene.dat[1,45:49]),levels=c("0","1"))])
points(cofactor.x,cofactor.y-1,pch=22,cex=3,lwd=2,bg=c('white',chamaelcol)[factor(t(gene.dat[2,45:49]),levels=c("0","1"))])
points(cofactor.x,cofactor.y-2,pch=22,cex=3,lwd=2,bg=c('white',rubrumtempcol)[factor(t(gene.dat[3,45:49]),levels=c("0","1"))])
points(cofactor.x,cofactor.y-3,pch=22,cex=3,lwd=2,bg=c('white',rubrumpolarcol)[factor(t(gene.dat[4,45:49]),levels=c("0","1"))])
#text(cofactor.x-.3,cofactor.y+.6,colnames(gene.dat)[2:10],srt=45,pos=4)
text(rep(min(cofactor.x)-.3,4),c(min(cofactor.y),min(cofactor.y)-1,min(cofactor.y)-2,min(cofactor.y)-3),c('M. pulex','M. chamaeleon','M. rubrum (temperate)','M. rubrum (polar)'),pos=2)
text(min(cofactor.x)-5,min(cofactor.y)+2,'Cofactor and Vitamin',cex=1.8,col='gray50',pos=4)


points(energy.x,energy.y,pch=22,cex=3,lwd=1,bg=c('white',MP)[factor(t(gene.dat[1,28:33]),levels=c("0","1"))])
points(energy.x,energy.y-1,pch=22,cex=3,lwd=2,bg=c('white',MC)[factor(t(gene.dat[2,28:33]),levels=c("0","1"))])
points(energy.x,energy.y-2,pch=22,cex=3,lwd=2,bg=c('white',tMR)[factor(t(gene.dat[3,28:33]),levels=c("0","1"))])
points(energy.x,energy.y-3,pch=22,cex=3,lwd=2,bg=c('white',pMR)[factor(t(gene.dat[4,28:33]),levels=c("0","1"))])
#text(energy.x-.3,energy.y+.6,colnames(gene.dat)[11:19],srt=45,pos=4)
text(rep(min(energy.x)-.3,4),c(min(energy.y),min(energy.y)-1,min(energy.y)-2,min(energy.y)-3),c('M. pulex','M. chamaeleon','M. rubrum (temperate)','M. rubrum (polar)'),pos=2)
text(min(energy.x)-5,min(energy.y)+2.1,'Energy',cex=1.8,col='gray50',pos=4)

```




## R Markdown


